Discrete Probability for Discrete Quantum Computing

### 2016-05-04 prob.tex
simple explanation of intervals perhaps

In this case, we split the $[0,1]$ interval into a collection of
overlapping closed sub-intervals obeying certain restrictions to be
described at the end of the section. First we illustrate the main
ideas using a simple example.

\begin{example}[Two-coin probability space with four intervals] \label{ex3}
We split the unit interval $[0,1]$ in the following four closed sub-intervals:
\begin{itemize}
\item $[0,0]$ which we call \imposs, 
\item $[0,\frac{1}{2}]$ which we call \unlikely, 
\item $[\frac{1}{2},1]$ which we call \likely, and 
\item $[1,1]$ which we call \necess.
\end{itemize}
Using these new values, the probability measure becomes:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
Not only does this probability measure reveal that the second coin is
double-headed but it also reveals the bias in the first coin, again despite
the absence of any numeric information.  
\qed\end{example}

The probability measure above can be understood in reference to
Ex.~\ref{ex1} by mapping each numeric value to the smallest interval
containing it. The probability measure appears quite intuitive from
that perspective. However, we also must be able to understand the
probability measure independently of Ex.~\ref{ex1} and in particular
justify how combinations such as
\[ 
\pmeas(\{HH\}) = \unlikely, \quad\pmeas(\{TH\}) = \likely, \quad
\pmeas(\{HH\}\cup\{TH\}) = \necess 
\]
which assert that an \unlikely-event whose probability is in the range
$[0,\frac{1}{2}]$ and a \likely-event whose probability is in the
range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
is in the range $[1,1]$! To understand this mystery, we look at
another more general example and then give the formal mathematical
definition of interval-valued probabilities.

\amr{See A Simple View of the Dempster-Shafer Theory of Evidence and 
  its Implication for the Rule of Combination Lotfi A. Zadeh, AAAI,
  1986}

\begin{example}[Dempster-Shafer Theory of Evidence] We have five
  employees whose precise age is not known. All is given is a range for
  each employee:
\[\begin{array}{rcl}
\textrm{Age}(M_{1}) & \in & [22,26]=D_{1}\\
\textrm{Age}(M_{2}) & \in & [20,22]=D_{2}\\
\textrm{Age}(M_{3}) & \in & [30,35]=D_{3}\\
\textrm{Age}(M_{4}) & \in & [20,22]=D_{4}\\
\textrm{Age}(M_{5}) & \in & [28,30]=D_{5}
\end{array}\]
What is the probability that an employee's age is in the range
$[20,25]$? Looking at the data, it is \emph{possible} for $M_1$'s age
to be within the range, it is \emph{not possible} for $M_3$'s age to
be within the range, and it is \emph{certain} or \emph{necessary} that
$M_4$'s age is in the range. Clearly saying that an event is
\emph{necessary} is equivalent to saying that its complement is
\emph{not possible}. Aggregating the results for the five employees,
we can calculate that is necessary that 2 employees have their ages
within the range, and it is possible that 3 employees have their ages
within the range. We express this formally as saying that the
probability of the event is $[0.4,0.6]$. Now consider another event
asking whether the ages are some other disjoint range
$[26,40]$. Reasoning in a similar way we calculate that the
probability for this event is $[0.4,0.6]$. Now let's take the two events
together and ask about the possibility of the ages to be in the range
$[20,40]$. Clearly that probability must be $[1,1]$ as every
employee's age is in that range. The way to calculate this probability
from the individual probabilities of the events is as follows: 
\begin{itemize}
\item \amr{can you try to fix this... perhaps it is not consistent
    with the interval-valued formalization but it is really nice if we
    can make it work}
\item Because ages are all integers, and we only consider ages from 20 to
40. Hence, the sample space~$\Omega$ can be $\left\{ 20,21,\ldots,39,40\right\} $,
and the set of events are $2^{\Omega}$ as usual.\\
\yutsung{I have numerically verified if we set $\Omega=\left\{ 20,22,25,26,28,30,35,40\right\} $,
and the answer should be the same as $\left\{ 20,21,\ldots,39,40\right\} $
because only end-points should matter in the question... I will numerically
verify $\left\{ 20,21,\ldots,39,40\right\} $, or prove they are the
same later...} 
\item Given a event~$E\subseteq\Omega$, the probability of $E$ can be
defined by 
\[
\pmeas(E)=\left[\frac{1}{5}\left|\left\{ i\middle|D_{i}\cap E\ne\emptyset\right\} \right|,\frac{1}{5}\left|\left\{ i\middle|D_{i}\subseteq E\right\} \right|\right]\textrm{ ,}
\]
where $\left|A\right|$ is the number of elements in $A$. Then, we
can verify that $\pmeas$ in an interval-value probability measure.
\end{itemize}
\qed\end{example}

In interval-valued probability measures, if the probability of an
event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
representing the strength of the evidence that supports $E$, and the
right-endpoint~$b$ as the strength of the evidence that contradicts
$E$.

Thus if we have an event $E$ with probability $[a,b]$ where
$a=0.1$ and $b=0.7$, we have that:
\begin{itemize}
\item the strength of evidence supporting $E$ is 0.1; since either $E$
  or its complement must happen, we conclude that there is 0.9
  evidence supporting the complement of $E$; 
\item the strength of evidence contradicting $E$ is 0.7; again since
  either $E$ or its complement must happen, we conclude that there is
  0.3 evidence contradicting the complement of $E$.
\end{itemize}

\yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
Homotopy Type Theory people said anything about the probability?}

Turning things around, the strength of evidence that contradicts
$E$ is evidence supporting the complement of $E$. The complement of $E$ must
therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:

\begin{eqnarray*}
\pmeas\left(\emptyset\right) & = & \imposs\\
\pmeas\left(\Omega\right) & = & \necess\\
\pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
\end{eqnarray*}
Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
then 
\begin{itemize}
\item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
\end{itemize}
Notice that the equality may not hold in general. This statement says
that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
putting all the evidences of $E_{i}$ together, but some evidence
may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
$\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
but may not equal. In our example, 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
 & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
\end{eqnarray*}
However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
because if we check the complement of $\{HH,TH\}$, we have 
\begin{eqnarray*}
 &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
\end{eqnarray*}
and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
of $\{HH\}$ and $\{TH\}$ individually.

>>>>

A natural generalization of the disjoint set-valued measure above is
to allow the sets to overlap. In this case, we split the interval
$[0,1]$ in a collection of \emph{overlapping} closed
sub-intervals. First we illustrate the main ideas using a simple
example.

\begin{example}[Two-coin probability space with four
  intervals] \label{ex3} We split the unit interval $[0,1]$ in the
  following four closed sub-intervals: $[0,0]$ which we call \imposs,
  $[0,\frac{1}{2}]$ which we call \unlikely, $[\frac{1}{2},1]$ which
  we call \likely, and $[1,1]$ which we call \necess.  Using these new
  values, we can modify the probability measure of Ex.~\ref{ex1} by
  mapping each numeric value to the smallest sub-interval containing
  it to get the following:
\[
\begin{array}{c@{\qquad\qquad}c}
\begin{array}{rcl}
\pmeas(\emptyset) & = & \imposs\\
\pmeas(\{HH\}) & = & \unlikely\\
\pmeas(\{HT\}) & = & \imposs\\
\pmeas(\{TH\}) & = & \likely\\
\pmeas(\{TT\}) & = & \imposs\\
\pmeas(\{HH,HT\}) & = & \unlikely\\
\pmeas(\{HH,TH\}) & = & \necess\\
\pmeas(\{HH,TT\}) & = & \unlikely
\end{array} & \begin{array}{rcl}
\pmeas(\{HT,TH\}) & = & \likely\\
\pmeas(\{HT,TT\}) & = & \imposs\\
\pmeas(\{TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH\}) & = & \necess\\
\pmeas(\{HH,HT,TT\}) & = & \unlikely\\
\pmeas(\{HH,TH,TT\}) & = & \necess\\
\pmeas(\{HT,TH,TT\}) & = & \likely\\
\pmeas(\{HH,HT,TH,TT\}) & = & \necess
\end{array}\end{array}
\]
This probability measure is more informative than the one in
Ex.~\ref{ex2}: not only does it reveal that the second coin is
double-headed but it also reveals the bias in the first coin.
\qed\end{example}

The probability measure above appears quite intuitive but it is not
really evident that it is well-defined. For example, how do we justify
the following combination of assignments:
\[ 
\pmeas(\{HH\}) = \unlikely, \quad\pmeas(\{TH\}) = \likely, \quad
\pmeas(\{HH\}\cup\{TH\}) = \necess 
\]
which assert that an \unlikely-event whose probability is in the range
$[0,\frac{1}{2}]$ and a \likely-event whose probability is in the
range $[\frac{1}{2},1]$ combine to a \necess-event whose probability
is in the range $[1,1]$. To understand the calculation, we provide the
formal definition of a probability measure in this case.

Fix a collection $\mathscr{I}$ of closed sub-intervals of $[0,1]$ that
must include $[0,0]$ and $[1,1]$. An $\mathscr{I}$--interval-valued
probability measure is a function
$\mu : \events \rightarrow \mathscr{I}$ such that:
\begin{itemize}
\item $\mu(\emptyset) = [0,0]$, 
\item $\mu(\Omega) = [1,1]$, and 
\item for any mutually disjoint events $E_1$, $E_2$, $E_3$, and $E_4$
  where $\pmeas(E_i) = [l_i,h_i]$ and where
  $E_1 \cup E_2 \cup E_3 \cup E_4 = \Omega$, we have:
\[
\pmeas(\{E_1\cup E_2\}) \subseteq
  [\max(l_1+l_2 , 1-(h_3+h_4)), \min(h_1+h_2 , 1-(l_3+l_4))]
\]
We view the events $E_1$ and $E_2$ as providing evidence for the
combined event $E_1\cup E_2$: their values set positive bounds on the
resulting interval. But as $E_3 \cup E_4$ is the complement of
$E_1 \cup E_2$, the events $E_3$ and $E_4$ provide negative bounds on
the resulting interval. The calculated interval may not be in our
fixed set $\mathscr{I}$ of chosen intervals so we embed it in the
smallest existing interval.
\end{itemize}

% to think of the above combination in the context of the evidence
% against the events established by the dual events. Writing in terms of
% the explicit intervals we see:
% \[\begin{array}{rcl@{\qquad}rcl}
% \pmeas(\{HH\}) & = & [0,\frac{1}{2}] & \pmeas(\{HT\}) & = & [0,0] \\
% \pmeas(\{TH\}) & = & [\frac{1}{2},1] &  \pmeas(\{TT\}) & = & [0,0]
% \end{array}\]
% The probability for $\pmeas(\{HH,TH\})$ is $[X,Y]$ where $X$ comes
% from the positive evidence for $\{HH\}$ and $\{TH\}$ and from the
% evidence against  is $[X,Y]$ where $X$ comes
% \[
% [\max(1,\frac{1}{2}),\min(1,\frac{3}{2})]
% \]

% must be at least as strong as the
% evidence for $\{HH\}$ and $\{TH\}$ individually and hence we have the
% tentative bounds on $\pmeas(\{HH,TH\})$ as
% $[\frac{1}{2},\frac{3}{2}]$. The dual events, however, establish
% evidence against $\{HH,TH\}$ with bounds $[

% A=HH
% B=TH
% C=HT
% D=TT

% To calculate the probability of $\{HH\}\cup\{TH\}$ we gather 
% evidence not only from the events $\{HH\}$ and $\{TH\}$, but also from 
% the dual events $\{HT,TH,TT\}$ and $\{HH,HT,TT\}$. The minimal
% probability for $\{HH\}\cup\{TH\}$ is\max(

% To understand this mystery, we look at
% another more general example and then give the formal mathematical
% definition of interval-valued probabilities.

% \begin{example}[Dempster-Shafer Theory of Evidence] We have three
%   employees whose precise ages $A_1$, $A_2$, and $A_3$ are not
%   known. All is given is a range of ages for each employee:
%   $A_1 \in \{ 23,24 \}$, $A_2 \in \{ 20,21,22\}$, and
%   $A_3 \in \{ 21,22 \}$. The sample space in this case is
%   $A_1 \times A_2 \times A_3$ which represents all the possible
%   combinations of ages for the three employees:
% \[\begin{array}{rcl}
% \Omega &=& \{ 
%         (23,20,21), (23,20,22), (23,21,21), (23,21,22), (23,22,21), (23,22,22), \\
% && ~(24,20,21), (24,20,22), (24,21,21), (24,21,22), (24,22,21), (24,22,22) \}
% \end{array}\]
% Subsets of $\Omega$ represent events as usual. Consider the event
% $\Omega$ that \emph{some} employee's age is in the range
% $\{20,21,22\}$: since that event covers the entire sample space its
% probability must be 1. We can however produce a more informative
% answer by reasoning as follows: it is \emph{impossible} for the first
% employee's age to be in the range $\{20,21,22\}$; it is \emph{certain}
% that the second employee's age is in that range; and it is
% \emph{possible} that the third's employee age is in that
% range. Aggregating the results, we see that it is \emph{necessary} for
% one out of three employees to have their age in the required range,
% and it is \emph{possible} for an additional employee to have their age
% in the required range. We summarize this information by reporting that
% the probability of this event is $[\frac{1}{3},\frac{2}{3}]$ where the
% first number reports the \emph{certainty} of the event and the second
% reports the \emph{possibility} of the event. We could also have
% reasoned about the dual event that \emph{no} employee's age is in the
% range $\{20,21,22\}$ to get the probability $[\frac{1}{3},\frac{2}{3}]$

%  dually
% about the evidence \emph{against} the event. The probability in this
% case

% Now consider the event
% that some employee's age is in the range $\{23,24\}$. Reasoning as
% above, the probability of this event is $[\frac{1}{3},\frac{1}{3}]$ as
% only the first employee qualifies. Clearly if we were to ask the
% probability that some employee's age is in the range
% $\{20,21,22,23,24\}$ the result should be $[1,1]$ as this range covers
% all the possibilities. The way to calculate this result from the two
% previous ones is as follows: the evidence for the combined event to be
% necessary is at least as strong as the evidence that each disjoint
% event that contributes to it is necessary. So the lower bound
% probability for the combined event is at least
% $\frac{1}{3}$. Similarly the upper bound probability is at least
% $1$. But now we can reason using the complements of the events about
% the necessity and possibility of refuting each event. For the event
% that some employee's age is \emph{not} in the range $\{20,21,22\}$ we
% have a probability $[\frac{1}{3},\frac{1}{3}]$ because it is necessary
% that $A_1$ is not in that range. Similary, the event that some employee's age is
% \emph{not} in the range $\{23,24\}$ is
% $[\frac{2}{3},\frac{2}{3}]$. Thus although the positive evidence for
% necessity

% \qed\end{example}

% \newpage

% \begin{example}[Dempster-Shafer Theory of Evidence] We have five
%   employees whose precise age is not known. All is given is a range for
%   each employee:
% \[\begin{array}{rcl}
% \textrm{Age}(M_{1}) & \in & \{ 23,24 \}=D_{1}\\
% \textrm{Age}(M_{2}) & \in & \{ 20,21,22\}=D_{2}\\
% \textrm{Age}(M_{3}) & \in & \{ 20,21 \}=D_{3}
% \end{array}\]
% What is the probability that an employee's age is in the range
% $\{22,23,24\}$? Looking at the data, it is \emph{possible} for $M_2$'s age
% to be within the range, it is \emph{not possible} for $M_3$'s age to
% be within the range, and it is \emph{certain} or \emph{necessary} that
% $M_1$'s age is in the range. Clearly saying that an event is
% \emph{necessary} is equivalent to saying that its complement is
% \emph{not possible}. Aggregating the results for the three employees,
% we can calculate that is necessary that 1 employees have their ages
% within the range, and it is possible that 2 employees have their ages
% within the range. We express this formally as saying that the
% probability of the event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now consider
% another event asking whether the ages are some other disjoint range
% $\{20,21\}$. Reasoning in a similar way we calculate that the
% probability for this event is $\left[\frac{1}{3},\frac{2}{3}\right]$. Now let's
% take the two events together and ask about the possibility of the ages to be in the range
% $\{20,21,22,23,24\}$. Clearly that probability must be $[1,1]$ as every
% employee's age is in that range. This problem
% looks puzzle if we want to attack it directly, but will be more clear
% if we think in terms of conditional probability. We will compute the
% conditional probability for the usual real-valued probability first
% and for the interval-valued probability later.
% \begin{itemize}
% \item We randomly draw an employee among the three, so each employee has
% probability $\frac{1}{3}$ to be drawn, i.e.,
% \[
% \pmeas\left(\left\{ i=1\right\} \right)=\pmeas\left(\left\{ i=2\right\} \right)=\pmeas\left(\left\{ i=3\right\} \right)=\frac{1}{3}
% \]
% In order to compute the usual real-valued probability, we need a probability
% distribution within the possible range $D_{1}$, $D_{2}$, and $D_{3}$.
% Let's assume they are equally probable, i.e., 
% \[
% \begin{array}{c@{\qquad\qquad}c}
% \begin{array}{rcl}
% \pmeas\left(\left\{ \textrm{Age}(M_{1})=23\right\} \right) & = & \frac{1}{2}\\
% \pmeas\left(\left\{ \textrm{Age}(M_{1})=24\right\} \right) & = & \frac{1}{2}
% \end{array} & \begin{array}{rcl}
% \pmeas\left(\left\{ \textrm{Age}(M_{2})=20\right\} \right) & = & \frac{1}{3}\\
% \pmeas\left(\left\{ \textrm{Age}(M_{2})=21\right\} \right) & = & \frac{1}{3}\\
% \pmeas\left(\left\{ \textrm{Age}(M_{2})=22\right\} \right) & = & \frac{1}{3}
% \end{array}\end{array}\begin{array}{rcl}
% \pmeas\left(\left\{ \textrm{Age}(M_{3})=20\right\} \right) & = & \frac{1}{2}\\
% \pmeas\left(\left\{ \textrm{Age}(M_{3})=21\right\} \right) & = & \frac{1}{2}
% \end{array}
% \]
% Then, the probability that an employee's age is in the range $\{22,23,24\}$
% can be computed as follow:
% \begin{eqnarray*}
%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
%  & = & \frac{1}{3}\cdot1+\frac{1}{3}\cdot\frac{1}{3}+\frac{1}{3}\cdot0=\frac{4}{9}
% \end{eqnarray*}
% \item Assume we don't know the probability distributions within the possible
% range $D_{1}$, $D_{2}$, and $D_{3}$. All we know is whether they
% are \emph{possible} or \emph{necessary}. Then we replace the above
% computation from exact value to interval and consider
% \begin{eqnarray*}
%  &  & \pmeas\left(\left\{ i\middle|\textrm{Age}(M_{i})\in\{22,23,24\}\right\} \right)\\
%  & = & \pmeas\left(\left\{ i=1\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{1})\in\{22,23,24\}\right\} \right)\\
%  &  & +\pmeas\left(\left\{ i=2\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{2})\in\{22,23,24\}\right\} \right)\\
%  &  & +\pmeas\left(\left\{ i=3\right\} \right)\pmeas\left(\left\{ \textrm{Age}(M_{3})\in\{22,23,24\}\right\} \right)\\
%  & = & \frac{1}{3}\cdot[1,1]+\frac{1}{3}\cdot[0,1]+\frac{1}{3}\cdot[0,0]=\left[\frac{1}{3},\frac{2}{3}\right]
% \end{eqnarray*}
% \yutsung{Check the conditional probability rule in the Dempster-Shafer
% Theory!}
% \end{itemize}
% \qed\end{example}

% In interval-valued probability measures, if the probability of an
% event $E$ is $[a,b]$, we think of the left-endpoint~$a$ as
% representing the strength of the evidence that supports $E$, and the
% right-endpoint~$b$ as the strength of the evidence that contradicts
% $E$.

% Thus if we have an event $E$ with probability $[a,b]$ where
% $a=0.1$ and $b=0.7$, we have that:
% \begin{itemize}
% \item the strength of evidence supporting $E$ is 0.1; since either $E$
%   or its complement must happen, we conclude that there is 0.9
%   evidence supporting the complement of $E$; 
% \item the strength of evidence contradicting $E$ is 0.7; again since
%   either $E$ or its complement must happen, we conclude that there is
%   0.3 evidence contradicting the complement of $E$.
% \end{itemize}

% \yutsung{Do we use the law of excluded middle here? You remind me Agda : ) Did
% Homotopy Type Theory people said anything about the probability?}

% Turning things around, the strength of evidence that contradicts
% $E$ is evidence supporting the complement of $E$. The complement of $E$ must
% therefore have probability $\left[1-b,1-a\right]$ which we abbreviate $1-\left[a,b\right]$:

% \begin{eqnarray*}
% \pmeas\left(\emptyset\right) & = & \imposs\\
% \pmeas\left(\Omega\right) & = & \necess\\
% \pmeas\left(\Omega\backslash E\right) & = & 1-\pmeas\left(E\right)
% \end{eqnarray*}
% Next, if we define $\sum_{i}\left[a_{i},b_{i}\right]=\left[\sum_{i}a_{i},\sum_{i}b_{i}\right]$,
% then 
% \begin{itemize}
% \item for a collection $E_{i}$ of pairwise disjoint events, we have $\pmeas\left(\bigcup_{i}E_{i}\right)\subseteq\sum_{i}\pmeas\left(E_{i}\right)$. 
% \end{itemize}
% Notice that the equality may not hold in general. This statement says
% that the evidences of $\bigcup_{i}E_{i}$ is at least as strong as
% putting all the evidences of $E_{i}$ together, but some evidence
% may only be acquired for $\bigcup_{i}E_{i}$ as the whole. Therefore,
% $\pmeas\left(\bigcup_{i}E_{i}\right)$ is a subset of $\sum_{i}\pmeas\left(E_{i}\right)$,
% but may not equal. In our example, 
% \begin{eqnarray*}
%  &  & \pmeas(\{HH,TH\})=\necess=[1,1]\\
%  & \subseteq & \left[\frac{1}{2},\frac{3}{2}\right]=\left[0,\frac{1}{2}\right]+\left[\frac{1}{2},1\right]=\unlikely+\likely=\pmeas(\{HH\})+\pmeas(\{TH\})\textrm{ .}
% \end{eqnarray*}
% However, $\pmeas(\{HH,TH\})$ is a proper subset of $\pmeas(\{HH\})+\pmeas(\{TH\})$
% because if we check the complement of $\{HH,TH\}$, we have 
% \begin{eqnarray*}
%  &  & \pmeas(\{HH,TH\})=1-\pmeas(\{HT,TT\})=1-\imposs=\necess\textrm{ ,}
% \end{eqnarray*}
% and $\pmeas(\{HT,TT\})=\imposs$ cannot be used to reasoning the probability
% of $\{HH\}$ and $\{TH\}$ individually.
